---
title: "Tutorial"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
gradethis::gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```


## Question 1

### Creating a vector {data-progressive=TRUE}

Create an atomic vector named `some_numbers` that contains the following numbers: 6,8,1,13 in that order. 

```{r question_1a, exercise=TRUE}

```


```{r question_1a-check}
grade_result(
  pass_if(~identical(.result, some_numbers<-c(6,8,1,13)))
)
```

### Changing values in a vector 

Change the second element of `some_numbers` to be equal to 88. 

```{r question_1b_setup}
some_numbers<-c(6,8,1,13)
```

```{r question1_b, exercise=TRUE,exercise.setup="question_1b_setup"}

```

```{r question1_b-solution}
#Solution code
some_numbers[2]<-88
```

```{r question1_b-check}
grade_code()
```

### Changing values in a vector 



## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

